Summary Tables

### 2021-07-14 summary_tables.Rmd
Regen

|bangalore|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 65.5|21.2|1.3 |
| cycle | 2.0|8.7|1.0 |
| car | 1.1|4.0|5.8 |
| motorcycle | 5.8|31.7|54.0 |
| bus | 24.0|30.6|34.7 |

>>>>

|bangalore|0-2 km|2-6 km|6+ km|
|---|---|---|---|
| pedestrian | 89.3|2.6|0.1 |
| cycle | 3.3|10.1|0.6 |
| car | 0.2|5.3|6.6 |
| motorcycle | 1.0|35.4|60.9 |
| bus | 4.4|40.2|29.7 |
